Understanding Cannabis Usage in Canada: Consistent Demographic Patterns in Cannabis Use Across Canada May Positively Correlate to High Frequency Use

### 2023-04-05 outputs/paper/paper.qmd
delete reference

In 2018, the Canadian government, led by Prime Minister Justin Trudeau, made the landmark decision to legalize the use of marijuana after a century of prohibition. While this move was praised as a step towards progressive drug policy by some, others expressed concerns about the potential negative effects on public health. Of particular concern was the potential increase in cannabis usage rates among the general population, especially young adults who would be at a higher long-term risk of negative health outcomes similar to those associated with tobacco, such respiratory issues, impaired cognitive development, and addiction.

>>>>

In 2018, the Canadian government led by Prime Minister Justin Trudeau, made the landmark decision to legalize the use of marijuana after a century of prohibition. While this move was praised as a step towards progressive drug policy by some, others expressed concerns about the potential negative effects on public health. Of particular concern was the potential increase in cannabis usage rates among the general population, especially young adults who would be at a higher long-term risk of negative health outcomes similar to those associated with tobacco, such respiratory issues, impaired cognitive development, and addiction.
